Erosion of somatic tissue identity with loss of the X-linked intellectual disability factor KDM5C

### 2024-07-24 submission/manuscript.Rmd
make margins larger

---
title:  Erosion of somatic tissue identity with loss of the X-linked intellectual disability factor KDM5C
output: pdf_document
geometry: margin = 0.5in
font-size: 11pt
header-includes:
   - \usepackage{caption}
   - \captionsetup[figure]{font=footnotesize, labelfont=bf}
   - \usepackage{sectsty} 
   - \usepackage{helvet}
   - \renewcommand{\familydefault}{\sfdefault}
   - \usepackage{lineno}
   - \linenumbers
   - \renewcommand\linenumberfont{\normalfont\small}
   - \usepackage{setspace}
   - \spacing{1.5}
   - \pagenumbering{arabic}
   - \usepackage{indentfirst}

>>>>

---
title:  Erosion of somatic tissue identity with loss of the X-linked intellectual disability factor KDM5C
output: pdf_document
geometry: margin = 1in
font-size: 11pt
header-includes:
   - \usepackage{caption}
   - \captionsetup[figure]{font=footnotesize, labelfont=bf}
   - \usepackage{sectsty} 
   - \usepackage{helvet}
   - \renewcommand{\familydefault}{\sfdefault}
   - \usepackage{lineno}
   - \linenumbers
   - \renewcommand\linenumberfont{\normalfont\small}
   - \usepackage{setspace}
   - \spacing{1.5}
   - \pagenumbering{arabic}
   - \usepackage{indentfirst}
